\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2013-01-05 paper/mswp2012-proposal.tex
updated with costs

\begin{tabular}{| p{3cm} | p{2cm} | p{2cm} | p{2.5cm} | p{2.5cm} | l |}
\hline
Member & Full-time / Part-time & Position & costs per hour & Duration & Overall costs \\
\hline
\hline
project manager & FT & manager & & start - end & \\
\hline
co-project manager &  FT & manager & & start - end  & \\
\hline
quality manger & FT & manager & & start - end  & \\
\hline
strategy memeber 4 & FT &  middle-manager & & start with version 1.0  & \\
\hline
strategy memeber 4 & FT &  middle-manager &  & start with version 1.0  & \\
\hline
reserarcher 1 &  FT  & & & start - end   & \\
\hline
reserarcher 2 & FT  & & & start - end  & \\
\hline
reserarcher 3 & PT & & & start - end  & \\
\hline
reserarcher 4 & PT & & & middle - end & \\
\hline
reserarcher 5 & PT & & & middle - end &  \\
\hline
security expert & FT & & & start - end &  \\ 
\hline
usability \& design engineer 1 + 2 & FT & & & start - end  & \\
\hline
web dev 1 & FT & & & dev \& update & \\
\hline
web dev 2 & FT & &  & dev \& update & \\
\hline
web dev 3 & FT & &  & dev & \\
\hline
web dev 4 & FT & &  & dev & \\
\hline
mobile dev 1 & FT & &  & dev \& update & \\
\hline
mobile dev 2 & FT & &  & dev \& update & \\
\hline
mobile dev 3 & FT & &  & dev & \\
\hline
mobile dev 4 & FT & &  & dev & \\
\hline
\end{tabular}

\subsection{Equipment}
Workplace with licenses consisting of:

\begin{itemize}
	\item {Computer}
	\item {Maus}
	\item {Tastatur}
	\item {Betriebssystem}
	\item {IDE}
	\item {...}
\end{itemize}
Makes around \EUR{1500} - \EUR{2000}  per employee. \\

\subsection{Material}
Once:\\
Printer in the Office 3 $\times$ \EUR{1500} \\
Testing devices (Android phones and iPhones) 4 $\times$ \EUR{500} \\
Books for research and development about \EUR{500} \\
Notebooks for managers 5 $\times$ \EUR{800} \\
\\
Monthly:\\
Server \EUR{50} by renting mailserver, fileserver and repository \\
Internet \EUR{50} \\
\\

@@

>>>>

\begin{tabular}{| p{3cm} | p{2cm} | p{2cm} | p{2.5cm} | l |}
\hline
Member & Full-time / Part-time & Position & Duration & Overall costs \\
\hline
\hline
project manager 1 & FT & manager & start - end & \EUR{140.000} \\
\hline
co-project manager 2 &  FT & manager & start - end  & \EUR{130.000} \\
\hline
quality manger 3 & FT & manager & start - end  & \EUR{130.000} \\
\hline
marketing manager 1 & FT &  middle-manager  & last 6 months  & \EUR{32.000} \\
\hline
marketing manager 2 & FT &  middle-manager  & last 6 months  & \EUR{32.000} \\
\hline
reserarcher 1 &  FT  & employee & start - end  & \EUR{80.000} \\
\hline
reserarcher 2 & FT  & employee & start - end  & \EUR{80.000} \\
\hline
reserarcher 3 & PT & employee & start - end  & \EUR{40.000} \\
\hline
reserarcher 4 & PT & employee & middle - end & \EUR{20.000} \\
\hline
reserarcher 5 & PT & employee & middle - end & \EUR{20.000}  \\
\hline
security expert & FT & expert & start - end & \EUR{130.000}  \\ 
\hline
usability \& design engineer 1 & FT & employee & start - end  & \EUR{80.000} \\
\hline
usability \& design engineer 2  & FT & employee & start - end  & \EUR{80.000} \\
\hline
web dev 1 & FT & employee & dev \& update & \EUR{60.000} \\
\hline
web dev 2 & FT & employee & dev \& update & \EUR{60.000} \\
\hline
web dev 3 & FT & employee & dev & \EUR{40.000} \\
\hline
web dev 4 & FT & employee & dev & \EUR{40.000} \\
\hline
mobile dev 1 & FT & employee & dev \& update & \EUR{60.000} \\
\hline
mobile dev 2 & FT & employee & dev \& update & \EUR{60.000}  \\
\hline
mobile dev 3 & FT & employee & dev & \EUR{40.000} \\
\hline
mobile dev 4 & FT & employee & dev & \EUR{40.000} \\
\hline
\end{tabular}

\subsection{Equipment}
	\begin{tabular}{| p{3cm} | p{2cm} | p{2cm} |}
		\hline
		workstation & member & costs \\
		\hline
		\hline
		Computer &  &  \\
		Maus &  &  \\
		Keyboard &  &  \\
		Display &  &  \\
		OS &  &  \\
		IDE &  &  \\
		%&  &  \\
		\hline
	\end{tabular}

\subsection{Material}
\begin{tabular}{| p{4cm} | p{2cm} | p{2cm} | p{2cm} | p{2cm} |}
	\hline
	name & amount & preparation & monthly & overall \\
	\hline
	\hline
	%&&&&\\
	%\hline
	Testing devices & 4 & \EUR{500} & 0 & \EUR{500} \\
	\hline
	Books (research, dev) & NA & \EUR{500} & 0 & \EUR{500}\\
	\hline
	Notebooks & 5 & \EUR{800} & 0 & \\
	\hline
	Printer & 3 & \EUR{1500} & 0 &\\
	\hline
	Server & 1 & 200 & 50 &  \\
	\hline
	Internet & 1 & 50 & 50 &  \\
	\hline
\end{tabular}
\\
TODO: Explanation Text

@@

das anwerben von partner benötigt einiges an reisen
zum bewerben des projektes gehört gereist
für die befragungen muss man an den ort der befragung reisen
